Competing Bandits: The Perils of Exploration under Competition

### 2018-09-05 paper/content/model.tex
Added a para on how our MAB instances are representative.

Before the game starts, each firm commits to an MAB algorithm, and uses this algorithm to choose its actions. Each algorithm receives a ``warm start": additional $T_0$ agents that arrive before the game starts, and interact with the firm as described above. \asedit{Each firm's objective is to maximize its market share: the fraction of users who chose this firm.}

@@

\subsubsection{MAB instances.}
In all experiments, there are $K=10$ arms. Since we focus on 0-1 rewards, an instance of the MAB problem is specified by the \emph{\MRV} $(\mu(a):\; a\in A)$. Initially the \MRV is drawn from some distribution, termed \emph{MAB instance}. We consider several representative MAB instances.
\begin{enumerate}
\item \emph{Needle-In-Haystack}: one arm (the ``needle") is chosen uniformly at random. This arm has mean reward $.7$, and the remaining ones have mean reward $.5$.

\item \emph{Uniform instance}: the mean reward of each arm is drawn independently and uniformly from $[0.25, 0.75]$.
\item \emph{Heavy-tail instance}: the mean reward of each arm is drawn independently from $\Beta(.6,.6)$ distribution.%
    \footnote{This distribution has substantial ``tail probabilities".}
\end{enumerate}

\subsubsection{Terminology.}
\asedit{Following a standard game-theoretic terminology, algorithm Alg1 \emph{(weakly) dominates} algorithm Alg2 for a given firm if Alg1 provides a larger (or equal) market share than Alg2 at the end of the game. An algorithm is a (weakly) dominant strategy for the firm if it (weakly) dominates all other algorithms. This is for a particular MAB instance and a particular selection of the game parameters.}

@@

\asedit{The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 XX Hz CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about XX hours.}

>>>>

Before the game starts, each firm commits to an MAB algorithm, and uses this algorithm to choose its actions. Each algorithm receives a ``warm start": additional $T_0$ agents that arrive before the game starts, and interact with the firm as described above. Each firm's objective is to maximize its market share: the fraction of users who chose this firm.

@@

\subsubsection{MAB instances.}
In all experiments, there are $K=10$ arms. Since we focus on 0-1 rewards, an instance of the MAB problem is specified by the \emph{\MRV} $(\mu(a):\; a\in A)$. Initially the \MRV is drawn from some distribution, termed \emph{MAB instance}. We consider three MAB instances:
\begin{enumerate}
\item \emph{Needle-In-Haystack}: one arm (the ``needle") is chosen uniformly at random. This arm has mean reward $.7$, and the remaining ones have mean reward $.5$.

\item \emph{Uniform instance}: the mean reward of each arm is drawn independently and uniformly from $[0.25, 0.75]$.
\item \emph{Heavy-tail instance}: the mean reward of each arm is drawn independently from $\Beta(.6,.6)$ distribution.%
    \footnote{This distribution has substantial ``tail probabilities".}
\end{enumerate}
\asedit{We argue that these MAB instances are (somewhat) representative. Consider the ``gap" between the best and the second-best arm, an essential parameter in the literature on MAB. The ``gap" is fixed in Needle-in-Haystack, spread over a wide spectrum of values under the Uniform instance, and is spread but  focused on the large values under the Heavy-Tail instance.}

\subsubsection{Terminology.}
Following a standard game-theoretic terminology, algorithm Alg1 \emph{(weakly) dominates} algorithm Alg2 for a given firm if Alg1 provides a larger (or equal) market share than Alg2 at the end of the game. An algorithm is a (weakly) dominant strategy for the firm if it (weakly) dominates all other algorithms. This is for a particular MAB instance and a particular selection of the game parameters.

@@

The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 \asedit{XX-Hz} CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about \asedit{XX} hours.
